---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BirdFlowExtras

<!-- badges: start -->
<!-- badges: end -->

**BirdFlowExtras** extends **BirdFlowR** with functions that are anticipated to 
be used by fewer users than the core functions; or that rely on packages that
are not on CRAN or Bioconductor and thus cannot be used by packages on CRAN.

## Installation

You can install the development version of BirdFlowExtras like so:

```r 
if(!require("remotes"))
  install.packages("remotes") 
remotes::install_github("birdflow-science/BirdFlowR")
```

## Example

Calculates Migratory Connectivity (MC) for a BirdFlowR model. This relies
on the **MigConnectivity** package to do most of the work.

```{r example}
library(BirdFlowExtras)
bf <- BirdFlowModels::amewoo
calc_birdflow_mc(bf, season = "postbreeding")

```

